Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-09 paper.tex
Revised the descriptio of example decision trees
#Closes 27

Please @7ossam81  and @JJ check this.
Maybe something else could be added to better interpret the models.

In this section we show the output of one of the models built during the regression, namely we present two of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate a useful decision-aid tool for and expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run). The first decision tree is considered for the publisher that sells the most. Figure \ref{fig:decision_tree_best_seller} depicts the decision tree for the best seller publishing company (UDL929). The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales. The second decision tree is for the same publishing company (the same data, but just considering the selected features by RAE method, since it is the one which yields the best results). The latter tree is shown in Figure \ref{fig:decision_tree_best_seller_fs}.

Examining both decision trees, it can be noticed that the \texttt{tot\_points\_sale} variable appeared twice in the tree and one of them was at the root. This indicates that the total number of points of sale has a major role in forecasting the total sales. We can also notice that \texttt{distrib\_novelty} appears at the top of the trees at a higher level compared to the \texttt{ret\_price} variable. In addition, both tree models reveal that marketing variables such as the total number of points of sale and the number of units distributed as novelty have higher influence on the prediction than the selling price of the book. This interpretation leads us to suggest that companies could probably improve the accuracy of their sales forecasting models by incorporating more marketing related variables in their models.

@@

In this paper, the problem of how many books should be printed 
when a new book is published is faced using several data-mining and
forecasting methods.

>>>>

In this section we show the output of one of the models built during the regression, namely we present two of the decision trees generated by M5P method applied to the data of the publisher that sells the most. These aim to demonstrate the value of the proposal to generate a useful decision-aid tool for an expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).

First, Figure \ref{fig:decision_tree_best_seller} depicts the decision tree for the publishing company UDL929. The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales. 
The second decision tree (Figure \ref{fig:decision_tree_best_seller_fs}) corresponds to the same publishing company, so the same data were used, but the RAE feature selection method was applied. Thus, the main difference in the simplification of the regression models in the second tree and the remove of \texttt{print\_run} as part of the decision process after the feature selection.

Examining both trees, it can be noticed that \texttt{tot\_points\_sale} variable appears twice in the trees, being also the root. This indicates that the total number of points of sale has a big influence on the decision models and also a major role in forecasting the total sales. This is an interesting clue for the experts, who could check the expected impact of different number of selling points
According to the trees, \texttt{distrib\_novelty} has also a big repercussion, appearing at the second level of the top of the trees.

An important fact that these tree models reveal is that marketing variables, such as the total number of points of sale and the number of units distributed as novelty have higher influence on the prediction than the selling price of the book, which could be, initially, considered as one of the most important parameters to determine sales. This interpretation leads us to suggest that companies could probably improve the accuracy of their sales forecasting models by incorporating more marketing related variables in their models.

@@

In this paper, the problem of how many books should be printed 
when a new book is going to be published is faced using several data-mining and
forecasting methods.
